A search for the production of Higgs pairs in the decay channel
$HH \rightarrow \gamma\gamma b\bar{b}$ is reported both for
resonant and nonresonant production. The data corresponds to an integrated
luminosity of 19.7 fb$^{-1}$ of proton-proton collisions at $\sqrt{s}=8$~TeV collected by the
CMS detector at the CERN Large Hardron Collider.
The candidate events are selected by requiring two photons and two jets and are classified
according to the number of jets tagged as coming from the hadronization of b-quarks.
The search for resonance production of two Higgs
through a new particle $X$, as hypothesized in extensions
to the Standard Model involving the Radion or KK-graviton from models with warped extra dimensions
or a heavy Higgs from models with supersymmetry,
is performed on the range $m_X \in [260, 1100]$~GeV.
The search for Standard Model nonresonant production of two Higgs is performed; in addition
a theoretical framework is explored for the analysis of anomalous values of the couplings
$t\bar{t}H$, $HHH$, and $t\bar{t}HH$.
The observations are consistent with expectations from Standard Model processes.
Upper limits at 95\% confidence level are extracted on the production cross section
of resonant and SM nonresonant production.
In particular, the Radion with $\Lambda_R = 1$~TeV is observed (expected) to be excluded with masses
below 0.97 TeV (0.88 TeV), while the analysis is not sensitive to the Radion with $\Lambda_R = 3$~TeV.
The nonresonant double Higgs cross section is observed (expected) to be excluded at
1.91 fb (1.59 fb) or 72.9 (60.7) times the NNLO Standard Model value.
These results are subsequently compared to different theories of beyond the Standard Model physics.
