This thesis would not have been possible without the input of many along the way.

First, I would like to thank my advisor Dan Marlow, who has guided me through all of my graduate
studies. I have profited immensely from our conversations about
particle physics and other topics. Sometimes, I was fortunate to be working with Dan on the same
project, and other times I was fortunate to have Dan's guidance as an external reviewer. At all
times, I have benefited from his ability to deconstruct problems and ask probing questions
while giving me the freedom to seek answers on my own accord.
I have seen that performing research occasionally involves
more than understanding the underlying physics,
and Dan's advice in navigating the bureaucracies created by
CMS and the Graduate School has been refreshingly helpful.

I would like to thank the professors in the Princeton Physics Department. In particular
I owe thanks to Chris Tully for discussions related to this thesis and for serving as a second reader.
and to Igor Klebanov and Peter Meyers for serving on committees for my FPO and pre-thesis project.

From my time at Purdue as an undergraduate, I would like to thank my advisor Daniela Bortoletto and
Artur Apresyan. Through the Higgs search at CDF,
their influence and patience gave me a strong desire to
see just how deep the rabbit hole goes (in the form of graduate study).
%particle physics was an interesting and worthwhile endeavor.

At CERN, I have had the privilege to work with many talented physicists. In the HggHbb group,
through which the main result of this thesis was achieved, I have had the pleasure to collaborate with
Olivier Bondu, Maxime Gouzevitch, Chiara Rovelli, Badder Marzocchi, Alexandra Oliveira, and
Amina Zghiche. I would especially like to thank Olivier for forcing the use of GitHub in our group,
ultimately making collaboration easier and more enjoyable.

I owe thanks to many others with whom I have collaborated on other CMS projects.
I would like to thank
from the luminosity subsystem, Nadia Adam, Andrzej Zuranski, Adam Hunt, and Paul Lujan;
from the Pixel Luminosity Telescope, Dean Hidas, Steve Schnetzer, Bob Stone, Andreas Kornmayer, and Andres Delannoy;
from the $W'$ analysis, Christos Leonidopoulos and Sunghyun Chang; and
from the $VH(b\bar{b})$ analysis Seth Zenz and Michael Mooney.

I would like to thank the friends over the years who have made life as or even more interesting
than my physics life. 
To those that comprise Centipede, Alex Tuna and Javier Duarte, I hope, nay expect, nay demand,
that we will run Boston one day.
To those in the V-card, Tuna and Kurt Brendlinger,
despite never wanting to use that awful (awesome?) name,
thanks for accepting me off the streets of Geneva as one of your own.
To Sven Rohr, I just realized that your future child is perhaps the first infant
I will take an interest in.
To those at Princeton, especially Aris Alexandradinata, Tim Lou, and Eric Smith,
every time I visited we picked up as if I never left.
To my brahs at the 400, Glen Klink, Cody Nelson, and Erik ``Ocho Cinco'' Stahoviak,
the last time I visited a portrait studio in the mall was for our family pictures.
Special recognition goes to Tuna, Kurt, Josh Hardenbrook, and Josh Kunkle for contributing
to multiple versions of our CERN relay team -- bestowed with the names Seal Team Six, $\Delta$F,
and Hostage Rescue Team -- and, in turn, creating a true American dynasty.
Heros are forged in the fires.

La langue française occupe un endoit special pendant le temps que j'ai passé comme doctorat.
Au moment que j'ai su que je démenagerais à Genève, j'ai commencé à l'apprendre avec l'aide de
plusieurs personnes patientes et encourageantes d'abord à Princeton et puis à Genève,
des professeurs ainsi que des amis.
Je remercie Brian Jacobs, Emilie Coquelin, Roberto Daverio, la Croix-Rouge genevoise,
et Liliane Munther.

I would like to thank my family whom I have been very fortunate to have by my side through ups and
downs. To my brothers, Craig and Jared, for many years of laughter and fighting, and
to my parents, for always providing a place to call home, I appreciate your constant support
and look forward to what the future has in store for us.
As the great philosopher Vin Diesel once said in a movie I'd wished I'd missed,
``Family is everything.''

Finally, to my fiancée Jigisha Darbha, thanks.
Your companionship has provided me many opportunities to grow as a person, and
when times are rough, you help me to think clearly.
I am excited that we will soon be officially on the same team.
As always, I ask for your patience while I slowly learn the language of your ancestors.
(Thanks to Siriesha for the translation.)
I look forward to many more adventures in Ireland, India, USA, and wherever else
public transport may take us.


This material is based upon work supported by the National Science Foundation
Graduate Research Fellowship under Grant No. DGE 1148900
and by the US Department of Energy under Grant No. DOE DE-SC0007968.
