
\chapter{Conclusion\label{ch:conclusion}}

Double Higgs production is a possible key to discovering physics beyond the Standard Model.
The process can be motivated either through the production of a new resonance decaying to
a Higgs pair or through the couplings $\lambda$, $y_t$, or $c_2$,
which effect the nonresonant production of a Higgs pair. The SM values for these couplings are
$\kapl = 1$, $\kapt = 1$, and $\ctwo = 0$. The search also provides a means
to test the SM through the measurement of the Higgs trilinear self-coupling, giving
more insight into the nature of the Higgs potential. However, the SM rate is too low
for current experiments to be sensitive to it. Preliminary estimates indicate that a factor of
$\mathcal{O}(100)$ more data is needed at the relevant LHC experiments in order to achieve
SM sensitivity.

With the current data, a search for the production of Higgs pairs is performed
by the CMS Collaboration in the decay channel $HH \rightarrow \ggbb$ using 19.7~fb$^{-1}$
of $pp$ collisions collected at $\sqrt{s} = 8$~TeV.
For the search of resonant production, masses under consideration are in the range between 260 GeV
and 1100 GeV. The selected events are divided into two categories based on the number of jets
consistent with the hadronization of b-quarks.
A simultaneous fit is performed in each category to the $\Mgg$ spectrum for resonant masses
below 400 GeV and to the $\Mggjjk$ spectrum for resonant masses above 400 GeV, and the results
in each category are combined. The observations are consistent with expectations from Standard
Model backgrounds, and upper limits at the 95\% confidence level are placed on the production
cross section. The limits are compared to the predictions from theories beyond the Standard Model,
such as the Radion and KK-graviton from models with warped extra dimensions or the heavy Higgs
from models with supersymmetry. The Radion with $\Lambda_R = 1$~TeV is observed (expected) to be
excluded with masses below 0.97 TeV (0.88 TeV), and the RS1 KK-graviton is observed to be
excluded with masses between 340 GeV and 400 GeV.

For the search of SM double Higgs production, a fit to the $\Mgg \times \Mjj$ plane 
is performed. The selected events are divided into four categories based on the number of jets
consistent with the hadronization of b-quarks and the value of the four-body mass.
The observations are consistent with expectations from the Standard Model backgrounds, and an
upper limit at the 95\% confidence level is placed on the production cross section.
The observed (expected) upper limit on the production cross section is 1.91 fb (1.59 fb),
or 72.9 (60.7) times the NNLO SM cross section. In addition, a theoretical framework is described
for the future study describing how anomalous couplings change the production cross section.
