\chapter{Systematic Uncertainties\label{ch:uncertainties}}

The expected signal yield is estimated through simulation with corrections for various effects.
These corrections are related the reconstruction and identification of photons and jets as well as
and to the b-tagging of jets.
The uncertainties associated with these corrections are applied to the reconstructed objects in
the simulation through scaling and smearing the observables of interest.
For the recorded luminosity, the normalization uncertainty is 2.6\%~\cite{CMS-PAS-LUM-13-001}.
In addition to the uncertainties related to photons and jets, covered in
Sections~\ref{sec:photonunc} and \ref{sec:jetunc}, respectively, theory uncertainties are imposed
on the resonant background, where the expected yield is also taken from simulation. These are covered
in Section~\ref{sec:theoryunc}.


\section{Photon Uncertainties\label{sec:photonunc}}

The photon-related uncertainties consist of those pertaining to the photon energy resolution (PER)
and the photon energy scale (PES)~\cite{CMS-PAS-HIG-13-001}. As a function of the photon
electromagnetic shower shape and $\eta$,
an uncertainty between 0.23\% and 0.93\% is imposed on the PER,
and an uncertainty between 0.12\% and 0.88\% on the PES. For hard photons, namely those with
$p_{{\rm T}} > 100$~GeV, the uncertainty on PES is increased to 1\%.
%These uncertainties are propogated through to the spectra of interest. For the $\Mgg$ spectrum,
%they give  uncertainties on the position and spread of the signal shape. For the
%$\Mggjjk$ spectrum, they give uncertainties on both the position and spread of the signal shape
%and on the normalization.

The photon preselection efficiency contributes a 1\% normalization uncertainty to the $\Mgg$
spectrum. The diphoton trigger efficiency contributes a 1\% normalization
uncertainty to all spectra.
An additional normalization uncertainty of 5\% is imposed in the high-mass resonant search
to account for the differences in the $p_{\rm T}$ spectrum between photons of the signal
and the electrons from $Z\rightarrow e^+ e^-$ used to estimate the PES and PER and their
corresponding uncertainties.

\section{Jet Uncertainties\label{sec:jetunc}}

The jet energy scale (JES) uncertainty is found by varying the jet $p_{\rm T}$ by 1--2\%,
depending on the jet $p_{\rm T}$ and $\eta$~\cite{JINST6}.
The jet energy resolution (JER) uncertainty is found by varying the jet resolution by 10\%.
In the high-mass search, the jets tend to have a higher boost and be closer together,
and effects related to their partial overlap are accounted for with an additional uncertainty of 1\%.
For the b-tagging efficiency uncertainty, the b-tagging scale factors are varied by one standard
deviation in each category~\cite{BTV}. 
The uncertainty for the b-tagging efficiency between the two categories
was found to have negative correlation.

\section{Theory Uncertainties\label{sec:theoryunc}}

No theory uncertainties are imposed for the resonant or nonresonant signal.
For the resonant background, theory uncertainties are imposed on the SM Higgs contribution. These
include contributions from missing order effects and the dependency on proton parton density
functions~\cite{Dittmaier:2011ti,LHC:SMHiggsBR}.
A systematic uncertainty is imposed on the Higgs mass for both for the resonant or nonresonant signal
and for the resonant background.
This uncertainty of 0.45 GeV is taken from the Higgs mass measurement performed at CMS in the
$H\rightarrow ZZ \rightarrow 4\ell$ channel~\cite{Chatrchyan:2013mxa}.

\section{Summary and Impact on Analysis\label{sec:uncimpact}}

The impact of the quoted systematic uncertainties is summarized in
Table~\ref{table:systematics_lowmass} for the low-mass resonant search and
Table~\ref{table:systematics_highmass} for the high-mass resonant search.
For the nonresonant search, uncertainties on the jets are
associated with the $\Mjj$ shape (parametric shift and resolution) rather than acceptance.
The analysis is statistically limited, and the systematic uncertainties worsen the expected sensitivity
by at most 1.7\% (3.8\%) in the resonant (nonresonant) search.

\begin{table}[htbp!]
  \centering
  \renewcommand{\arraystretch}{1.4}
  \caption{Systematic uncertainties for the low mass resonant search.}
  \input{tables/systematics_lowmass}
  \label{table:systematics_lowmass}
\end{table}

\begin{table}[htbp!]
  \centering
  \renewcommand{\arraystretch}{1.4}
  \caption{Systematic uncertainties for the high mass resonant search.}
  \input{tables/systematics_highmass}
  \label{table:systematics_highmass}
\end{table}
